\newpage
\section{Achieving Active Status} To achieve active status for the current semester, a Michigan Gamma Tau Beta Pi member must satisfy one of the following:
\begin{enumsubsection} %maybe change numbering type
\itemnotoc	Be an officer, Distinguished Active, or Prestigious Active,
\itemnotoc	Have initiated into the society in the current semester, or,

%\itemnotoc	Have returned to campus at the start of the current semester, and had been active prior to leaving, or

\itemnotoc	Achieve a sufficient level of activity in the society, as defined by the following requirements:
\begin{enumsubsubsection}
\itemnotoc	Attend, at a minimum, two meetings, both of which must be  voting meetings (2nd Actives, 3rd Actives or Officer Elections),
\itemnotoc	Complete two hours of TBP-sponsored service, and
\itemnotoc	Attend at least one social event or serve as a mentor in the chapter mentorship program.
\end{enumsubsubsection} 
\end{enumsubsection} 
Members who have completed all requirements for active status apart from attendance at voting meetings may be considered a Temporary Active if sufficient voting meetings remain for the member to achieve active status for that semester. Temporary Active status is only maintained through the duration of voting meeting for which it is granted. 

In addition, any alumni member must request active status each semester, in accordance with \href{http://www.tbp.org/off/ConstBylaw.pdf}{C-VI of the Constitution of the Tau Beta Pi Association}.

\section{Maintaining Active Status} Active status is maintained through the end of the semester following the semester in which it is achieved, provided that the member has attended at least one chapter meeting that semester. Those who leave campus may maintain active status upon their return provided they achieved active status the semester prior to leaving and attend at least one chapter meeting during the semester when they return.

\section{Tracking Status}  Active status is evaluated by the Membership Officer.  If an inactive member satisfies the above requirement mid-semester, he/she can also be made active immediately upon request.  

\section{Benefits of Active Status}  Active status may be designated on some chapter documents, and may be used in determining eligibility for certain chapter benefits at the discretion of the officer corps.  However, inactive members do not lose privileges (other than voting) relating to standard meetings and socials.
