\section{General Meetings}\label{sec:genmeetings} General meetings will be scheduled and held in the Fall Term and in the Winter Term: Each Semester there must be at least a general actives meeting, one candidate informational meeting, two election of candidates meetings,  an election of officers meeting, and the formal initiation. The Executive Committee may schedule additional meetings as appropriate. The general meeting schedule will be published prior to the first day of class each semester.

%The following regular meetings will be scheduled and held once in the Fall Term and once in the Winter Term: a general actives meeting; two candidate informational meetings (``comities"); two election of candidates meetings; three electee/actives meetings; an election of officers meeting; and the formal initiation.  The regular meeting schedule will be published prior to the first meeting of each semester.

\section{Officer/Advisor Meetings} Officer/advisor meetings are held to update all officers on chapter
matters and confirm general meeting agendas.  In general, the
officer/advisor meetings should be held before scheduled regular
meetings, and whenever else needed at the discretion of the President.
There must be at least three officer/advisor meetings and one
officer/advisor transition meeting.

\section{New Initiatives Meetings} \label{sec:NImeetings}
These meetings are to be held throughout the semester for the purpose of proposing and brainstorming new opportunities for the chapter to become involved in the University and Ann Arbor communities, as well as future projects and directions for the chapter.  This can include opportunities related  to recruiting new members, improving chapter image, and providing additional professional development activities.

\section{Special Meetings} Special meetings may be called at any time by the President, by any chapter advisor, or upon written request to the President signed by five active members. If any official business is to be conducted at the meeting, notice of at least one week must be provided to the general membership.
