%%Need to copy in Article VIII
\resetformat
\begin{optionalpart}
\part{Relevant Sections of National Constitution}
\begin{center}
{\bf Article VI\\
Collegiate Chapters}
\end{center}
SECTION 5. {\bf Control}. Each Chapter shall have full control of its individual affairs, subject 
to this Constitution and the Bylaws of the Association. A Chapter shall enact Bylaws for its 
own guidance, and such Bylaws shall not be in conflict with this Constitution or the Bylaws 
of the Association and shall not be suspended except with the written consent of a majority 
of the Advisory Board of the Chapter. Internal business of a chapter may be conducted in 
its local language and currency. See Bylaw V, Sec. 5.03 (d) (6). \\[1em]
SECTION 6. {\bf  Officers}. The officers of each Chapter shall be a President, a Vice-President, 
a Recording Secretary, a Corresponding Secretary, a Treasurer, and a Cataloger, who shall 
be active members of the Chapter, and four alumnus advisors, all of whom shall be elected 
by the Chapter. The duties of these officers shall be those usually performed by persons 
holding such offices, and as the Constitution and Bylaws of the Association and the Bylaws 
of the Chapter shall prescribe. See Bylaw V.\\[1em]
SECTION 7. {\bf Advisory Board}.
\begin{enumerate}
\item The Advisory Board of the Chapter shall consist of 
the President, the Vice-President, and the Corresponding Secretary of the Chapter, and the 
four alumnus advisors elected by the Chapter. In first organizing the Advisory Board of 
any Chapter, the four alumnus members shall be elected to serve for periods of one, two, 
three, and four years respectively, and thereafter one member shall be elected each spring, 
to hold office for four years. See Bylaw V, Sec. 5.03 (h).
\item The Advisory Board shall act as an advisory and judiciary committee to determine the 
advisability of any action taken or proposed by the Chapter. Such action may be referred to 
it by a vote of the Chapter or brought before it by a petition of a minority of the same, or the 
Board may review such action on its own initiative. All changes in the Bylaws of a Chapter 
must be submitted to, and approved by, the Advisory Board before going into effect. The 
Advisory Board, by a majority vote, may forbid any such action or change, subject to an 
appeal to the Executive Council of the Association.
\end{enumerate}
SECTION 8. {\bf Proxy}. A member of a Chapter shall not be allowed to vote by proxy.\\[1em]
SECTION 9. {\bf Meetings}. Each Collegiate Chapter may arrange for and hold such meetings as it desires, but at least one business meeting and one general meeting of a social, 
literary, or technical character shall be held each term, quarter, or semester, except in the 
summer, in addition to the meetings held for the consideration, election, and initiation of 
candidates for membership.\\[1em]
\part{Relevant Sections of National Bylaws}
\setcounter{chapter}{5}
\setcounter{section}{3}
\begin{center}
{\bf Bylaw 5\\
Collegiate Chapters}
\end{center}
SECTION 5.01. {\bf  Election of Officers}.
\begin{enumerate}
\item There shall be an election of Chapter officers as early 
in the calendar year as conditions allow. They shall take office at least one month before the annual 
spring convocation or commencement. The policy of holding one additional election each year may 
be established with the approval of the Chapter's Advisory Board at the discretion of the Chapter. 
Officer vacancies shall be filled in accordance with the Chapter's officer-election procedure.
\item The retiring officers shall turn over all the records to their successors and these records 
shall be up-to-date in all regards. It shall be the first duty of all incoming officers to familiarize 
themselves with these records and to see that they are in good order and up-to-date, and, if not, 
to try to get the cooperation of their predecessors before the latter leave college permanently.
\item The records shall include the roll and record books, the minutes of the meetings of 
the Chapter for the current and previous years, the Treasurer's accounts for the current and 
previous years, the files of the Corresponding and Recording Secretaries, holders containing 
a complete file of the copies of THE BENT and of THE BULLETIN for the last three years, 
the card or other catalogs of the active and inactive members and of the alumnus members 
of the Chapter, and a correct and itemized list of the paraphernalia and other properties of 
the Chapter pertaining to the initiation ceremonies with note as to their place of storage. 
Older issues of THE BENT may be offered to the library of the institution.
\item An elected officer of the Chapter may be removed for cause. Sufficient cause for 
removal may include, but is not limited to: having continued unexcused absences from the
meetings of the Chapter; not attending to assigned or elected duties of the Chapter; inexcusably 
failing to meet financial obligations to the Chapter; violating the Constitution and Bylaws of 
the Association or the Bylaws of the Chapter; violating a rule, practice, or procedure adopted 
by the Chapter; or displaying conduct deemed contrary to the interests of the Chapter. 
\begin{enumerate}
\item Any member(s) who wish(es) to remove an alleged offending officer shall notify a Chapter 
Advisor, who shall convene a meeting of the Advisory Board to consider the charge(s). Any 
charged officer who is a member of the Advisory Board shall be excluded from the meeting.
\item If the Advisory Board decides that a charge has merit which warrants removal from 
office, the charged officer will be suspended from all duties as an officer. The Advisory 
Board shall provide the officer in question with the opportunity to defend the charge(s) in 
a formal hearing at which counsel may represent the charged officer.
\item The Advisory Board shall adopt rules and format to ensure due process, compose a statement 
of charge(s), notify the charged officer that a suspension has occurred, and establish a time and place 
for the hearing where the charge(s) will be considered. At least 21 days in advance of the hearing date, 
the Chapter must notify the Secretary-Treasurer and confirm that the charged officer has received 
these items or send them by registered mail to the last recorded address of the charged officer.
\item After the hearing has been conducted and considered, the Advisory Board shall, by 
majority vote, recommend whether or not to remove the charged officer. The Advisory Board 
shall call a meeting of the active membership at which it will present its recommendation.
\item The Chapter may remove the charged officer by a two-thirds vote from at least onehalf of the active members of the Chapter. Unless a majority votes to remove the charged 
officer, he or she shall be reinstated to office immediately.
\item A removed officer may appeal the decision to the Executive Council. 
\item If a charged officer resigns from office at any time during this process, the removal 
process shall cease immediately.
\end{enumerate}
\end{enumerate}
SECTION 5.02. {\bf Standing Committees.}\\ Each Chapter shall have standing committees on 
Membership, Initiation, Program, Social Activities, and such other committees as the Chapter 
shall desire and establish. Except by special Chapter action by three-fourths majority vote, the 
President of the Chapter shall decide upon the size of each of the committees and shall appoint 
its membership, preferably after conference with the appointed chair of the committee.\\[1em]
Section 5.03. {\bf Duties of Officers}.
\begin{enumerate}
\item It shall be the duty of the President, as the responsible 
agent and leader of the Chapter, to see that the other officers of the Chapter perform their duties in 
accordance with the Constitution and Bylaws of the Association and the Bylaws of the Chapter.
\item The Vice President of the Chapter shall be the chair of the Program Committee and shall have as 
a special duty the advancement of the technical and professional education of the active members.
\item It shall be the duty of the Recording Secretary to keep the roll and record books of the 
Chapter as obtained from the Secretary of the Association, the minutes of the meetings of 
the Chapter completely written up-to-date and to keep in a suitable holder all the issues of 
THE BENT for the last three years and also in a similar holder all issues of THE BULLETIN
for the last three years for the use of the members of the Chapter.
\item It shall be the duty of the Corresponding Secretary of each Chapter to:
\begin{enumerate}
\item Send promptly in October each year to the Secretary-Treasurer of the Association lists 
of the names and post-office addresses of the officers of the Chapter and to report promptly all 
changes in this information which may occur during the year. See B. VIII, Sec. 8.01(a), (b).
\item Send to the Secretary-Treasurer of the Association the Report of Eligibility as 
specified in Bylaw VI, Sec. 6.05(a). See Bylaw VIII, Sec. 8.01(c).
\item Send to the Secretary-Treasurer of the Association the Report of Election and card forms entitled Tau Beta Pi Catalog Card as specified in Bylaw VI, Sec. 6.05(b). See Bylaw VIII, Sec. 8.01(d).
\item Send to the Secretary-Treasurer of the Association the Report of Final Action as 
specified in Bylaws VI, Sec. 6.05(c), and VII, Sec. 7.07. See Bylaw VIII, Sec. 8.01(e).
\item Send to the Secretary-Treasurer of the Association, immediately upon receipt of 
the proper form or after their election, a duplicate of the credentials for the delegate and 
alternate to the ensuing Convention. See Bylaw VIII, Sec. 8.01(f).
\item Furnish to the Secretary-Treasurer of the Association a copy of the Chapter's Bylaws, amended to date, with the written approval of the Advisory Board within two weeks 
of their adoption and amendment. See Bylaw VIII, Sec. 8.01(g).
\item Report to the Secretary-Treasurer of the Association a receipt from the IRS for the 
appropriate 990 form as required. See Bylaw VIII, Sec. 8.01(h).
\item Report to the Secretary-Treasurer of the Association such items of news and of 
interest as to honors received, offices to which members of the Chapter have been elected, 
and the like, and also any cases of discipline which might affect the standing of one or more 
members on the rolls of the Association.
\item Carry on such other correspondence of the Chapter as the President may direct.
\item Report to the Secretary-Treasurer of the Association any and all actions taken by 
the Advisory Board of the Chapter. 
\end{enumerate}
\item ~
\begin{enumerate}
\item Within two weeks after each initiation, the Chapter, through its Treasurer, shall 
remit to the Secretary-Treasurer of the Association the stated amount of the initiation fee 
payable to the Association for each new initiate. See Bylaw VII, Sec. 7.04. This remittance 
shall cover the costs of the badge, certificate of membership, a four-year subscription to THE
BENT, a copy of the Constitution and Bylaws and other approved literature of the Association. 
It shall also include a sum for the necessary expenses of the Association, including the cost 
of publishing THE BULLETIN. The initiation fee shall be determined by the Convention, 
on recommendation of the Executive Council. Within two weeks after each initiation, the 
Chapter shall also remit to the Secretary-Treasurer the stated amount of the Convention 
assessment payable to the Association for each new initiate. See B-I, Sec. 1.05.
\item Except when the rules of the institution require that the Treasurer of a Chapter 
keep its financial accounts in a specified way and form, the official bookkeeping system of 
the Association on standard forms furnished by the Secretary-Treasurer of the Association 
shall be used and followed.
\item For any candidate not initiated, the Chapter shall be refunded or credited, as it may 
elect, the full amount of the remittance, excepting the actual cost of the certificate if it shall 
have been engrossed and of the badge if it shall have been engraved.
\end{enumerate}
\item The Cataloger of each Chapter shall keep an up-to-date catalog of its active and 
alumnus members, giving the full name, the home address, and the college address of each 
member and the names of the officers of the Chapter, including the Advisory Board.
\item It shall be the duty of every member to assure that each elective officer of the Chapter conscientiously performs the duties of the office for the benefit of the entire Chapter, 
particularly in matters pertaining to finance and the relations of the Chapter with the Secretary-Treasurer of the Association, and to take appropriate action when an elected officer 
fails to perform the duties of the office. See Bylaw V, Sec. 5.01 (d).
\item The primary duty of the alumnus advisors is to provide for continuity of Chapter 
operations. The alumnus advisors shall see that the Chapter:
\begin{enumerate}
\item Selects candidates who 
meet the eligibility requirements of Constitution Article VIII, the bylaws of the Chapter, 
and the academic regulations of the host institution. 
\item Balances its financial accounts and 
pays all bills by the end of the academic year. 
\item  Effects an orderly transition of Chapter 
officers in accordance with Bylaw V, Sec. 5.01. 
\end{enumerate}
\end{enumerate}
SECTION 5.04. {\bf Chapter Finances}.
\begin{enumerate}
\item The expenses of a Chapter shall be borne by the 
initiation fees, by dues to be paid each quarter, term, or semester, and by any assessments that the 
Chapter may decide. These assessments may be voted at any regular meeting of the Chapter by a 
three-fourths affirmative vote of all the active Chapter membership eligible to vote thereon, subject, 
on appeal, to the approval of the Advisory Board of the Chapter. See Con. Art. VI, Sec. 1.
\item Each Chapter shall decide on the amount of its initiation fee (including the stated 
amount of the initiation fee payable to the Secretary-Treasurer of the Association) and on 
its dues per quarter, term, or semester. See Const. Art. VI, Sec. 1.
\item The budget of the estimated expenses of the Chapter for the next college year shall 
be prepared in March or April by the officers of the Chapter. It shall be the special order 
of business of one of the regular April meetings of the Chapter. It shall include all of the 
expenses of the initiation ceremonies, dinners, luncheons, picnics, dances, and other social 
activities, back debts, prizes and awards, auditor and bank charges, loans to electees, Convention assessment, rents, supplies, long-distance telephone calls, stationery, postage, etc.
\end{enumerate}
SECTION 5.05. {\bf Convention Delegate}.
\begin{enumerate}
\item At one of the regular April meetings of the 
Chapter, after canvassing the subject to find out who can most conveniently go to, and to 
consider who will most satisfactorily represent the Chapter at, the next regular Convention 
of the Association, the Chapter's Convention delegate and an alternate shall be elected by 
the active members of the Chapter. See Bylaw I, Sec. 1.04.
\item On the delegate's return from the Convention, it shall be the delegate's duty to make 
a general report, preferably in writing, to the Chapter at its next regular meeting on the 
business transacted by the Convention, the entertainment received, and impressions of the 
Convention and the delegates, with suggestions for the improvement of the life and work 
of the Chapter and its members.
\end{enumerate}
SECTION 5.06. {\bf District Activities}.\\
 The Chapter shall cooperate with the Director(s) 
of the District to which it is assigned; shall inform the Director(s) of its activities; and shall 
participate in the activities of its District to the extent of the capability of its members.\\[1em]
SECTION 5.07. {\bf Quorum}.\\
 A quorum for the consideration of routine business shall consist 
of one-half the active membership of the Chapter; for the election of new members, for the 
revocation of election, for changing the initiation fee or Chapter dues, and for the passing of 
an assessment on the members of the Chapter, three-fourths of the active chapter membership 
eligible to vote thereon; and for the approval or disapproval of a proposed amendment to the 
Constitution or Bylaws of the Association or Chapter, three-fourths of the active members of 
the Chapter. See Const. Art. VI, Sec. 1. Chapters located at colleges operating on a cooperative basis and those chapters with evening division members may be granted permission by 
the Executive Council to lower the requirements listed above for a quorum.\\[1em]

\begin{center}
{\bf Bylaw 6\\
Election of Members}\\
Available at: \url{http://www.tbp.org/off/ConstBylaw.pdf}
\end{center}

\end{optionalpart}