\section{Record Maintenance and Transition} Records must be kept up-to-date and in good order. The complete records must be given  to the new officers at the officer/advisor transition meeting. The treasurer must turn over copies of his/her records; however, original records will be kept until after the treasurer files the appropriate tax return forms for the chapter. The current copies of the transition reports and the bylaws, as well as a reasonable revision history, will be maintained by the Advisory Board, with help from the Historian as appropriate.
\section{Authorized Signers} %Financial stewards?
 The chapter President, the Treasurer, and the Secretary will be signers on the chapter's Student Organization Account Services (SOAS) account. A fourth signer on the account will be either an officer or advisor and designated at the discretion of the other three signers.  
\section{Fiscal Year} The Chapter's fiscal year is January 1 to December 31.

\section{Chapter Budget} The Treasurer will propose a budget for approval by $\frac{5}{7}$ of the Advisory Board prior to the first meeting of the Advisory Board during the Fall and Winter Semesters. This budget will be constructed with the input of the officer corps and will be reviewed by the Executive Committee.  %The budget will consist of pools, each under the authority of a team, officer, or chair.}
\section{Spending Authority} No expenditures, in addition to the approved budget, will be made against the Chapter's accounts without the approval of the Treasurer and $\frac{5}{7}$ of the Advisory Board or their designee.
