\chapter{Name, Scope, and Precedence}

\section{Name}
This chapter is named ``Tau Beta Pi Association, Inc., Michigan Gamma Chapter", or equivalently, the Michigan Gamma Chapter of the Tau Beta Pi Association, hereafter referred to as ``Michigan Gamma" or simply, the ``chapter". The Tau Beta Pi Association, Inc. may hereafter be referred to as the ``Association."

\section{Scope}
This constitution governs the proceedings of the chapter in all matters not specifically provided for in the Constitution, Bylaws, and Convention Acts of the Association.
\section{Precedence} The governing precedence of the chapter is:

\begin{compactenum}[1.]
\itemnotoc  All rules and regulations of the University of Michigan and the College of Engineering that apply to honor societies.
\itemnotoc  The Constitution, Bylaws, and Convention Acts of the Association.
\itemnotoc This chapter constitution.
\itemnotoc Any Bylaws the chapter may enact.
\end{compactenum}

In the event of a conflict between  the rules and regulations of the University of Michigan and the College of Engineering and the Constitution, Bylaws, and Convention Acts of the Association this chapter will notify the Association of any such conflicts and of this chapter's action with regard to these conflicts. Unless otherwise stated, all official business of the chapter will  be conducted in accordance with Robert's ``Rules of Order" Revised, subject to the provisions of the governing precedence of the chapter.

\section{Terminology} This Constitution, together with any Bylaws enacted by the chapter, will collectively serve the role of chapter Bylaws as prescribed in C-VII, 4 of the Constitution of the Association.

\section{University Affiliation} The Michigan Gamma Chapter of Tau Beta Pi is, at the time of the ratification of this Constitution, a sponsored student organization and is sponsored by the College of Engineering - Office of Student Affairs. % Added in October 2017 to comply with CCI's ridiculous requirements for constitutions. This affiliation CAN change. It does not belong in a constitution.

%\section{Nondiscrimination}  \removed{The Michigan Gamma Chapter of Tau Beta Pi is committed to a policy of equal opportunity for all persons and does not discriminate on the basis of race, color, national origin, age, marital status, sex, sexual orientation, gender identity, gender expression, disability, religion, height, weight, or veteran status in its membership or activities.}% unless permitted by university policy for gender specific organizations. % proposed in 2023 due to CCI changing its mind.
