\chapter{Chapter Officers}
\section{}
The minimum set of chapter officers is defined in the \hkn Operations Manual.

\section{}
The officer corps has the power to make decisions affecting the day-to-day operation of the chapter between and during regularly scheduled chapter meetings.
Decisions not specifically delegated to an individual officer by the constitution or bylaws will bemade by a simple majority vote of the officer corps.

\section{}
Additional responsibilities of the required officers as well as additional officer positions may be specified in the chapter bylaws.

\section{}
Regular elections must be held once per each Fall and Winter academic semester.
The elections meeting must be announced to both active members and potential initiates at least one week in advance in the manner typical for chapter announcements.
Specific election procedures, including but not limited to time limits and order of individual elections, may be defined in the chapter bylaws.

\section{}
Newly elected officers shall take office at midnight on the first day following the prior semester's exam period.

\section{}
An officer may be removed from office for failing to perform his/her duties or for performing an act detrimental to Beta Epsilon chapter of \hkn.
A motion to remove an officer will be raised only upon a three-fourths majority of the remaining Officer Corps.
Removing an officer requires a three-fourths majority vote of the present and voting members at a general meeting and approval of the faculty advisor(s).
